   22-Aug-99 ........... SCAT  -  Scaler Dump Procedure ............. PAGE   1
 
 
 
   SCAT200  How to Copy CAMAC Scalers to Tape
 
   CAMAC  scalers  may be read and written to the data acquisition output tape
   during the data acquisition process. The following features are supported:
 
   (1)....Scalers to be  read  are  specified  in  exactly  the  same  way  as
          described  for  program  SCAD  (i.e. for real time display). See the
          SCAD section of the ORPHAS manual.
 
   (2)....Scaler records may be written to tape  at  timed  intervals  (10  to
          1000 seconds are allowed), preceeding file-marks or both.
 
   (3)....Scalers may be cleared after each reading if desired.
 
   (4)....The  date  and  time  of  the  scaler record dump is included in the
          record.
 
   (5)....Scaler records are 32000 bytes long and written in ASCII.
 
   (6)....Program lemo supports the retrival, display  and  logging  of  these
          records. While running lemo, Type: H LIST, to see relevant commands.
 
 
   (7)....The  maximum  number  of  scalers  supported  at this time (raw plus
          computed) is 790.
 
   User commands:
   ---------------------------------------------------------------------------
   SCAT  filename         ;Process "snit file"
 
   SCAT  ON               ;Dump before EOF only
   SCAT  ON  CLR          ;Dump before EOF and (clr post dump)
   SCAT  ON  TSEC         ;Dump every TSEC and before EOF
   SCAT  ON  TSEC  CLR    ;Dump every TSEC and before EOF (clr post dump)
   SCAT  OFF              ;Disable scaler dumps
 
   SCAT  NORT             ;Normalize count rates to internal clock
   SCAT  NORS             ;Normalize count rates as specified by snit-file
   SCAT  UNOR             ;Count rates un-normalized
 
   SCAT  STAT             ;Displays/logs setup status
   SCAT  HELP             ;Displays on-line help
   SCAT  H                ;Displays on-line help
 
   SCAT  LERR ON/OFF      ;Turns error display/logging ON
   SCAT  LERR OFF         ;Turns error display/logging OFF
 
   SCAT  ZERR             ;Zeros read-error  counters
   SCAT  ZDUM             ;Zeros scaler dump counter
   SCAT  ZERO             ;Zero all scalers
 
