   02-Feb-02 ....... U530  BANDO (UNIX & VMS versions) - WTM ........ PAGE   1
 
                      PROG TO EXAMINE AND MODIFIY BAN-FILES
 
   Program  BANDO  provides for the examination and/or modification of certain
   data contained in a ban-file. Some of it's features are:
 
   (1)....An input ban-file may be opened for examination  or  copying  to  an
          output file.
 
   (2)....An  output  ban-file  may   be   opened   for   examination   and/or
          modification. The output file cannot be the same as the input file.
 
   (3)....ID-numbers on the output ban-file may be changed.
 
   (4)....Bananas may be copied from the input- to the output-file.
 
   (5)....Bananas may be deleted from the output file.
 
   (6)....Bananas  in  the output file may be turned OFF. This sets the ID# in
          the   directory   negative  and  changes  the  label-fields  of  all
          entry-lines to OFF so that the entry will be ignored.
 
   (7)....Bananas may be turned ON. Reverses the action taken in (6).
 
   (8)....The numbers NUPM, IAUX & JAUX may be changed for specified IDs.
 
   (9)....The X- & Y-parameters (IPX,IPY) may be changed for specified IDs.
 
                 THE FOLLOWING LIST OF COMMANDS ARE WHAT YOU GET
 
   COMMAND       - ACTION OR MEANING
   IN   fil.ban  - Assign fil.ban for input
   OU   fil.ban  - Assign fil.ban for output
   NUOU fil.ban  - Create+Assign fil.ban for output
   DDRI          - Display input  file directory
   DDRO          - Display output file directory
   DI   ID       - Display FFG # ID from input
   DO   ID       - Display FFG # ID from output
   IO   IDI,IDO  - Input IDI output as IDO
   OFF  ID-LST   - Turn OFF ID-LST on output file
   ON   ID-LST   - Turn  ON ID-LST on output file
   DE   ID-LST   - Delete ID-LST from   output file
   COPY ID-LST   - Copy ID-LST from input to output
                 - ID-LST implies IDA,IDB,IDC.......
   REN  IDA,IDB  - Rename IDA to IDB on output file
   NUP  ID,I,J,K - Set NUPM..JAUX for ID on output
   PXY  ID,IX,IY - Set IPX,IPY    for ID on output
   HELP          - Gets this HELP-LIST again
   END           - Terminates program
 
   Type: bando               ;To start with bando defined in your
                             ;.login, .cshrc or login.com files, otherwise,
 
   Type: /usr/hhirf/bando    ;To start execution on a HHIRF DECstation
   or
   Type  /home/upak/bando    ;To start execution on a SPARCstation
   or
   Type: @U1:[MILNER]BANDO   ;To start execution on the HHIRF VAX
