   11-Sep-03 .......... U910  TXX - Text Formatting - WTM ........... PAGE   1
 
 
                A TEXT FORMATING PROGRAM FOR LINE PRINTER OR LN03
 
   Section  Contents
 
       010  Introduction
 
       020  Directives for Setup Which Contain Data
 
       030  Directives for Setup Which Contain no Data
 
       040  Directives for Processing text
 
       050  Text Imbedded Directives for Bold & Underline
 
       060  How to Use on VAX
 
       070  How to Use on a DECstation or SPARCstation
 
   U910.010  Introduction
 
   TXX  manipulates  alphameric  material  to form centered and side headings,
   single lines, and left and  right  justified  paragraphs  of  four  styles.
   Pages  may be specified to be any length and any width up to 75 characters.
   The input is typed starting in col. 1 and ending in any column  up  to  80.
   No  word  should  be  broken  (continued  from one line to the next) in the
   input text. Text formating is specified by the use  of  a  number  of  case
   insensitive  directives.  The  first  line  processed by TXX must contain a
   directive as must  the  last  line.  Only  the  first  4  characters  of  a
   directive  line  (i.  e.  the  directive itself) is processed unless stated
   otherwise in the following list. The following directives are recognized:
 
   U910.020  Directives for Setup Which Contain Data
 
    RPD$IIIJJJKKK
 
          Says set page dimension to be III  characters  wide  and  JJJ  lines
          long.  KKK  specifies  the  next  page number to use. If KKK is left
          blank, the page number sequence is  unchanged.  The  default  values
          are III=75, JJJ=56 and KKK=1.
 
    RSH$IIJJ
 
          Says  shift  pages  alternately  II  and  JJ  spaces  to  the  right
          (starting with II) - default is II=JJ=3
 
    RND$JJ  Sets indent or "outdent" to JJ spaces (default=7).
 
    NPS$JJ  Sets # of blank lines after page label to JJ (default=0).
 
    CHP$AAAA  Chapter Label
 
          Says set chapter# to AAAA - the first 4 characters  following  CHP$.
          AAAA  is inserted in the Section Labels as described below. AAAA and
          Chapter Label are used in page labels.
    
   11-Sep-03 .......... U910  TXX - Text Formatting - WTM ........... PAGE   2
 
 
   U910.020  Directives for Setup Which Contain Data (continued)
 
    SEC$NUM  Section Label
 
          Says replace the 4 characters SEC$ with Chapter# (AAAA).  and  print
          the resulting line image in BOLD UNDERLINED characters.
 
 
   U910.030  Directives for Setup Which Contain no Data
 
    NAS$  Says turn OFF automatic spacing       (see Note-1)
    ASP$  Says turn ON  automatic spacing       (default)
    NPL$  Says turn OFF automatic page labeling (see Note-2)
    PGL$  Says turn ON  automatic Page labeling (default)
    TPF$  Says do top-of-form (page eject)      (see Note-2)
    TOF$  Same as TPF$
    TON$  Says process TOF$ & TPF$ directives   (default)
    NOT$  Says ignore  TOF$ & TPF$ directives
    SIN$  Says use single spaced printing       (default)
    DBL$  Says use double spaced printing
    SPN$  Says print N blank lines (N=1,9)
    BON$  Turns BOLD      ON  for subsequent lines, paragraphs, etc.
    BOF$  Turns BOLD      OFF for subsequent lines, paragraphs, etc.
    UON$  Turns UNDERLINE ON  for subsequent lines, paragraphs, etc.
    UOF$  Turns UNDERLINE OFF for subsequent lines, paragraphs, etc.
    JON$  Turns right-justify of paragraphs ON  (default)
    JOF$  Turns right-justify of paragraphs OFF
    QIT$  Says end of all text - wrap it up and go home
 
 
   U910.040  Directives for Processing text
 
    CY1$  Says copy input lines to output lines unaltered
    CYB$  Same as CY1$ except prints bold
    COV$  Says copy input lines "verbatim" until COF$ encountered
    COF$  Says turn off "verbatim" copy
    CEN$  Says center contents of each input line on specified page
    CEB$  Same as CEN$ except prints bold
    INP$  Forms an    indented paragraph of following text
    BLP$  Forms a        block paragraph of following text
    ODP$  Forms an   outdented paragraph of following text
    FIP$  Forms fully indented paragraph of following text
   ------------------------------------------------------------------------
 
   Note-1:  Text  processing  directives (CY1$ thru FIP$, above) automatically
   insert one blank line unless otherwise requested by the NAS$ directive.
 
   Note-2: The TPF$ (or TOF$) directive normally starts a new page and  labels
   it  with the date, text from the CHP$ directive and a page number. The NPL$
   directive turns off page labeling.
    
   11-Sep-03 .......... U910  TXX - Text Formatting - WTM ........... PAGE   3
 
 
   U910.050  Text Imbedded Directives for Bold & Underline
 
   \B\ or \b\    ;Turns BOLD      ON  within a line or paragraph
 
   \U\ or \u\    ;Turns UNDERLINE ON  within a line or paragraph
 
   \BU\ or \bu\  ;Turns BOLD and UNDERLINE ON
 
   \UB\ or \ub\  ;Turns BOLD and UNDERLINE ON
 
   \\            ;Turns both OFF (back to state specified by BON$,
                 ;BOF$, UON$, UOF$, etc)
 
 
   U910.060  How to Use on VAX
 
   Create a text file, text.doc for example (the .doc  filename  extension  is
   required). Don't forget to end with QIT$.
 
   Type:  @U1:[MILNER]TXXL text   ;For automatic listing on LASER3
 
          Processes  text.doc,  responding  to all directives including bold &
          underline. A formatted file text.txx is produced and  submitted  for
          print/delete on LASER3.
 
   Type:  @U1:[MILNER]TXXP text   ;To generate text.txx
 
          Processes  text.doc,  responding  to  all  directives  except bold &
          underline. A formatted  file  text.tex  is  produced  which  can  be
          printed on any printer or viewed on the screen, etc.
 
 
 
 
   U910.070  How to Use on a DECstation or SPARCstation
 
   Create  a  text  file, text.doc for example (the .doc filename extension is
   required). Don't forget to end with QIT$. Assuming that  the  path  to  the
   txx executable is appropriately defined:
 
   Type: txx text X    ;To generate text.txx
 
          Processes  text.doc,  responding  to all directives including bold &
          underline. A formatted  file  text.txx  is  produced  which  can  be
          printed on an LN03 laser printer, etc.
 
   Type: txx text      ;To generate text.tex
 
          Processes  text.doc,  responding  to  all  directives  except bold &
          underline. A formatted  file  text.tex  is  produced  which  can  be
          printed on any printer or viewed on the screen, etc.
