   31-Mar-04 .... U620  FITU - A General 1-D Fitting Package - ...... PAGE   1
 
 
 
          A Spline, Linear & Non-Linear (least squares) Fitting Program
 
   ---------------------------------------------------------------------------
   Define:     Spline Fitting  =      Spline-Under-Tension Fitting
 
   Define:     Linear Fitting  =      Linear-Least-Squares Fitting
 
   Define: Non-Linear Fitting  =  Non-Linear-Least-Squares Fitting
   ---------------------------------------------------------------------------
 
 
   Sec Page Contents
 
   010   2  Introduction - for     Spline Fitting
   020   3  Introduction - for     Linear Fitting
   030   3  Introduction - for Non-Linear Fitting
   040   4  Introduction - Input Data Format
 
   050   5  Commands which Apply to Spline,  Linear & Non-linear Procedures
 
   060   6  Commands for Setup/Control of Spline Fitting
 
   070   7  Commands for Setup/Control of Linear Fitting
   080   8  Expanded Definitions of some  Linear Fitting Commands
   090   8  Definition of Some Output for Linear Fitting
 
   100   9  Commands for Setup/Control of Non-Linear Fitting
   110   9  A Brief Description of the    Non-Linear Fitting Procedure
 
   120  10  Template make-file (and Comments) for Customized Processes
   130  11  Example (default) Non-linear Support Routine - USERCMP
   140  15  Example (default) Non-linear Support Routine - USERFOX
 
   150  16  Commands Related to Filename Variables, Symbols and Loops
   160  17  Comments
 
 
 
                                    FOREWORD
 
   Program  FITU  is  an  enhanced  version  of program FUNKYFIT that provides
   graphical  displays  of  fit  results  of  Spline,  Linear  and  Non-Linear
   fitting.  User customization is supported for the Non-Linear process. There
   are some changes in the format of the output but the input data  format  is
   unchanged.
 
 
 
                               HOW TO GET STARTED
 
   ---------------------------------------------------------------------------
   Type:  fitu               ;To start if /usr/hhirf/ is defined in your
                             ;.login, or .cshrc files, otherwise:
 
   Type:  /usr/hhirf/fitu    ;To start on HRIBF Alpha or Linux platforms
   ---------------------------------------------------------------------------
    
   31-Mar-04 .... U620  FITU - A General 1-D Fitting Package - ...... PAGE   2
 
 
   U620.010  Introduction - for Spline Fitting
 
   The  spline fitting feature provided here uses a package of subroutines for
   computing "spline under tension" obtained from the following source:
 
          From Fitpack -- August 31, 1981
          Coded by A. K. Cline and R. J. Renka
          Department of Computer Sciences
          University of Texas at Austin
 
   There are three parameters which may be specified by the  user.  These  are
   S, EPS & SIGMA which are discussed below. Default values are:
 
   S     =  FLOAT(N)            ;Where N is the number of X,Y points to fit
   EPS   =  SQRT(2.0/FLOAT(N))
   SIGMA =  1.0
 
   S......contains  the  value  controlling  the  smoothing.  This   must   be
          non-negative.  For  S   equal   to   zero,   the   subroutine   does
          interpolation,  larger  values  lead  to   smoother   funtions.   If
          parameter  D  contains  standard  deviation  estimates, a reasonable
          value for S is FLOAT(N).
 
   EPS....contains a tolerance on the relative precision to which S is  to  be
          interpreted.  This  must  be  greater than or equal to zero and less
          than   or   equal   to   one.   A   reasonable   value  for  EPS  is
          SQRT(2.0/FLOAT(N)).
 
   SIGMA..contains the tension factor. This  value  indicates  the  degree  to
          which  the  first  derivative  part  of  the smoothing functional is
          emphasized. If SIGMA is nearly zero (e.g. .001) the resulting  curve
          is  approximately  a  cubic spline. If SIGMA is large (e.g. 50.) the
          resulting curve is nearly a polygonal line. If SIGMA equals  zero  a
          cubic spline results. A standard value for SIGMA is approx 1.
 
   Spline  fitting is probably most useful in providing smoothed interpolation
   of experimental data since it can "draw a curve"  through  almost  any  1-D
   data  set  with  increasing  X-values. It is not useful in characterizing a
   data set as being linear, quadratic,  cubic,  expodential,  etc.  since  it
   only  generates  an  array  of  parameters  (2nd  derivatives) equal to the
   number of data points.
 
   You can use the Spline Fitting feature of FITU to fit  your  data,  display
   the  fit,  and  adjust S, EPS & SIGMA and uncertainties until you like what
   you see and then utilize the Spline routines CURVS  &  CURV2  (included  in
   ORPHLIB) to interplolate the data for your own program.
 
   See ORPHLIB documentation SEC#480 for a description of CURVS & CURV2.
 
                                    Briefly:
 
   Use FITU to adjust S, EPS, SIGMA and uncertainties until you like the fit.
 
   Link  to  ORPHLIB  to  get  routines  CURVS & CURV2 to provide interpolated
   values to your oun probram.
 
                                   IMPORTANT!
 
   Maintain the same S, EPS, SIGMA and uncertainties as was used  by  FITU  to
   get the fit that you liked.
    
   31-Mar-04 .... U620  FITU - A General 1-D Fitting Package - ...... PAGE   3
 
   U620.020  Introduction for Linear Fitting
 
   FITU  is  a general purpose linear-least-squares fitting program which fits
   sets of (X,Y) points  to  a  linear  combination  of  up  to  20  algebraic
   functions. Directives are used to choose one of the following forms for the
   fit.
 
                  J=N
         Y(X) = SUM   B(J)*F(J,X)
                  J=1
 
                  J=N
         Y(X) = SUM   B(J)*F(J,LOG(X))
                  J=1
 
                       J=N
         LOG(Y(X)) = SUM   B(J)*F(J,X)
                       J=1
 
                       J=N
         LOG(Y(X)) = SUM   B(J)*F(J,LOG(X))
                       J=1
 
   Where  N  is  the  no. of terms (functions of X) and F(J,X) denotes the Jth
   function of X. B(J) denotes the Jth coefficient which is determined in  the
   fit.  Experimental  and  calculated  values, coefficients, errors and CHISQ
   values are listed.  Although  most  of  the  output  from  FITU  should  be
   self-explanatory, some quantities are defined in SEC#090.
 
 
 
   U620.030  Introduction for Non-Linear Fitting
 
   Non-Linear  fitting  of  data  to  a  function  Y(X) is carried out via the
   gradient search method. The user must create a customized version  of  FITU
   by  linking  a  user  supplied  REAL*8  function USERFOX which computes the
   function value and a user command processor USERCMP which supports it.
 
   o......Create a routine USERFOX to compute the value of  the  function  (or
          functions)  using  the value of X and the coefficient array A passed
          in the argument list.
 
   o......Create a user command processor USERCMP to support USERFOX.
 
   o......Note: that USERFOX can be a multi-function routine. In such a  case,
          USERCMP  can be used to select which function is actually used for a
          given fit request.
 
   o......Use   the  template  make-file  given  in  SEC#120  to  create  your
          customized version of FITU.
 
   See SEC#120 for a listing of the template make-file
 
   See SEC#130 for an example USERCMP
 
   See SEC#140 for an example USERFOX
 
   Note: that most of the functions in the example USERFOX  are  not  actually
   non-linear.  I  used  these  to check that linear and non-linear procedures
   gave nearly the same results.
    
   31-Mar-04 .... U620  FITU - A General 1-D Fitting Package - ...... PAGE   4
 
 
 
   U620.040  Introduction - Input Data Format
 
 
   Data to be fitted can be read from a  file  or  entered  interactively.  In
   either  case  the  format  is  the  same.  The  structure is illustrated as
   follows:
 
   ---------------------------------------------------------------------------
   DATA             ;Introduces Y vs X DATA-SET
   X  Y <YERR>      ;Up to 500 DATA-SET entries
   X  Y <YERR>
   .
   .
   ENDA             ;Ends DATA-SET
 
   DATA             ;Introduces Y vs X DATA-SET
   X  Y <YERR>      ;Up to 500 entries (X,Y values)
   X  Y <YERR>      ;YERR is optional
   .
   .
   ENDA             ;Ends this   DATA-SET
   ---------------------------------------------------------------------------
 
   The ACCII directive DATA Introduces a list  of  (X,Y,U)  or  (X,Y)  entries
   (i.e.  a  data  set).  Here  U denotes the uncertainty in Y. The first data
   point is on the line following the DATA  label.  Data  points  are  entered
   one-per-line  and  up to 500 points are allowed. The data set is terminated
   with an ENDA directive which must start in column  1.  The  ENDA  line  can
   contain no other information.
 
   The  file  can  contain  any number of data sets. The ordinal number of the
   data set is used to identify which data set is to be fitted.
    
   31-Mar-04 .... U620  FITU - A General 1-D Fitting Package - ...... PAGE   5
 
 
   U620.050  Commands which Apply to Both Linear & Non-linear Procedures
 
   CMD  Data-list   Definition or Action
   ---- ---------   ----------------------------------------------------
 
   H                Displays directory to on-line help
 
   LON              Says record all commands on log-file - fitu.log
   LOF              Says only record output  on log-file
 
   END              Ends program
 
   CMD  filnam      Open and process commands from filnam.cmd
   CMD  filnam.ext  Open and process commands from filnam.ext
 
   IN   filename    Open new data file (full filename required)
 
   CSUN             Says set uncertainties to be counting statistics
   ABUN             Says data-set uncertainties are in absolute units
   PCUN             Says data-set uncertainties are in %
   ALUN UVAL        Says set all uncertainties to UVAL(%)
   USUN UVAL        Says set unspecified uncertainties to UVAL(%)
   MULU FAC         Says multply all given uncertainties by FAC
 
   XMM  XLO,XHI     Sets display X-range (min & max)
   XMM              Sets display X-range defined by data
 
   YMM  YLO,YHI     Sets display Y-range (min & max)
   YMM              Sets display Y-range defined by data
 
   LIN              Set display to be linear
   LOG              Set display to be log (in the Y-direction)
 
   STAT             Displays/logs some setup parameters
 
   UCOM STAT        Displays/logs status provided by USERCMP
 
   WIN  ID          Specify window ID for next display of fit results
 
   REVV             Reverses Video (black-to-white, white-to-black)
                    You must do a FIG, then the REVV, and another FIG
                    for it to take effect.
 
   FIG  N           Execute a standard "FIG" - i.e. like damm
 
   CLR              Clears all FIGed windows
 
   XON              Says X-server (graphic display)   available (default)
   XOF              Says X-server (graphic display) unavailable
    
   31-Mar-04 .... U620  FITU - A General 1-D Fitting Package - ...... PAGE   6
 
 
   U620.060  Commands for Setup/Control of Spline Fitting
 
   CMD  Data-list   Definition or Action
   ---- ---------   ----------------------------------------------------
 
   S    VAL         Set smoothing parameter to VAL (default: VAL=NDAT)
 
   EPS  VAL         Set tolerance on parameter S   (default: VAL=SQRT(2/NDAT))
 
   SIG  VAL         Set tension parameter SIGMA    (default: VAL=1.0)
 
   SFIT ID          Request a spline fit to data set no. ID
 
   SVAL X           Request spline interpolated value at abcissa X
 
   SVAL X1 X2 DX    Request spline interpolated values for:
                    (X = X1 to X2 in steps of DX)
 
   SSTAT            Requests display/log of spline parameters
    
   31-Mar-04 .... U620  FITU - A General 1-D Fitting Package - ...... PAGE   7
 
 
   U620.070  Commands for Setup/Control of Linear Fitting
 
   CMD  Data-list   Definition or Action
   ---- ---------   ----------------------------------------------------
 
   LINX             Set to use FUNCS of X - F(X)      DFLT
 
   LOGX             Set to use FUNCS of Log(X) - F(Log(X))
 
   LINY             Set to fit Y to F(X) or F(LOG(X)) DFLT
 
   LOGY             Set to fit Log(Y) to F(X) or F(Log(X))
 
   XLIM XMIN,XMAX   Set fit-limits in terms of X-values
 
   ILIM IMIN,IMAX   Set fit-limits in terms of index-I
 
   NUFU             Says new Function (i.e sets #TERMS=0)
 
   XPOW E1,E2..     Exponent list for power-series terms
 
   LPOL J1,J2..     Ordinal-list for Legendre poly terms
 
   TABL XLO,XHI,DX  Specs for computed Y vs X table
 
   HFMT,DFMT        Table header & data formats (see SEC#080)
 
   *                A * in col-1 of a command line results in the full
                    line being copied to log-file as a comment
 
   FIT   ID         Fits set# ID
   FITU  ID         Same as above but UNWEIGHTED
                    (if ID is omitted, previously entered ID is used)
    
   31-Mar-04 .... U620  FITU - A General 1-D Fitting Package - ...... PAGE   8
 
 
   U620.080  Expanded Definitions of Some Linear Fitting Commands
 
   TABL...XMIN,XMAX,DELX (range & step-size for table of values of  calculated
          Y vs X). TABL without associated list deletes table request.
 
   XLIM...XMIN,  XMAX  (range  of  fit limits on X - default is no limit) XLIM
          without subsequent list gets rid of limit.
 
   ILIM...ILO,IHI (range of fit limits on data point ordinals - default is  no
          limit). ILIM without subsequent list gets rid of limit.
 
   XPOW...List  of  powers-of-X to be included as terms in the "fit function".
          For example; XPOW=0,1,2 says include the terms X**0, X**1  and  X**2
          (i.e. 1.0, X and X*X).
 
   LPOL...List  of  legendre polynomial "ordinals". For example; LPOL=2,4 says
          include the terms P2(X) and P4(X).
 
   HFMT...Heading FORMAT for first line of table of calculated values of Y  vs
          X. This line contains 10 entries (0.0, DELX, 2*DELX - - -9*DELX).
 
   DFMT...Data  FORMAT for subsequent lines of table of calculated values of Y
          vs X. These lines  contain  11  entries  (X-value  corresponding  to
          first Y-value and 10 Y-values).
 
          Note-  HFMT  and  DFMT  are not free-form entries. These labels must
          start in column 1 and the actual format must follow immediately.  No
          other  information  can be included on this line. Examples (also the
          defaults) are;
 
          HFMT(1H ,10X,10F10.3/)  and  DFMT(1H ,11F10.3)
 
   FIT....ID - says retrieve data set number ID from the input disk  file  and
          carry  out  a  fit as previously specified. If ID is not entered, it
          is assumed that the data set is already in memory (either  typed  in
          or  previously  retrieved from disk). Only one data set is in memory
          at any given time.
 
   FITU...has the same meaning as  FIT  except  that  the  fit  is  unweighted
          (actually all points are given equal weight - namely, unity).
 
 
   U620.090  Definition of Some Output for Linear Fitting
 
   FIT-ERR(%)  gives  the calculated uncertainty in the associated coefficient
          (determined in the fit) based on the quality of fit  (QFN)  and  the
          scatter of the data points about the calculated values.
 
   EST-ERR(%)  gives  the calculated uncertainty in the associated coefficient
          based on the quality of fit and the  scatter  of  experimental  data
          that  is  to  be expected based on the uncertainties assigned to the
          data.
    
   31-Mar-04 .... U620  FITU - A General 1-D Fitting Package - ...... PAGE   9
 
 
 
   U620.100  Commands for Setup/Control of Non-Linear Fitting
 
 
   CMD  Data-list   Definition or Action
   --------------------------------------------------------------------------
 
   UCOM STAT        Displays/logs status provided by USERCMP
 
   TOF  VN          Says turn fit-variable VN OFF
   TON  VN          Says turn fit-variable VN ON
 
   SKPI I J K ...   Says skip entry ordinals I J K in computing sum RESQ
   SKPI             Says remove all skips
 
   UCOM FUNK FID    Says select function# FID (in USERFOX) for fitting
 
   UCOM CPOS CID    Allows adjustable coefficient-CID to be positive only
 
   UCOM CPOM CID    Allows adjustable coefficient-CID to be pos or neg
                    (overrides default set in USERCMP until next UCOM FUNK
 
   NITF NIT         Sets # of iterations for coefficients for best fit
                    to NIT (default = 20, allowed values are 1 to 100)
 
   NITE NIT         Sets # of iterations for coefficient uncertainty estimate
                    to NIT (default = 10, allowed values are 1 to 100)
 
   GO   ID          Do a     non-linear fit on data set# ID
   GOMO ID          Continue non-linear fit of data set# ID
                    (if ID is omitted, previously entered ID is used)
 
 
   U620.110  A Brief Discussion of the Non-Linear Fitting Procedure
 
                  Procedure for Determining Coefficient Values
                  ============================================
 
   1......A   gradient  search  for  the  coefficients  giving  the  best  fit
          (smallest CHISQ) is carried out.
 
   2......The starting coefficient values are changed randomly from  the  best
          fit values by multiplying each by (1.5-RAN(ISEED)).
 
   3......Steps  1  and  2 are repeated NITF times and coefficients leading to
          the smallest CHISQ are recorded.
 
 
               Procedure for Estimating Coefficient Uncertainties
               ==================================================
 
   1......The input data is  randomly  modified  to  simulate  what  might  be
          expected  (from  the  assigned  data  point  uncertainties)  if  the
          experiment were repeated.
 
   2......A search for the best-fit coefficients is carried out.
 
   3......Steps   1   &   2  are  repeated  NITE  times  and  the  coefficient
          uncertainties   are  estimated  from  the  spread  in  the  best-fit
          coefficients computed in steps 1 & 2.
    
   31-Mar-04 .... U620  FITU - A General 1-D Fitting Package - ...... PAGE  10
 
 
 
   U620.120  Template Make-file (and Comments) for Customized Processes
 
   Template make-file found at /usr/hhirf/fitu.make
   ===========================================================================
   FFLAGS= -fpe2
   #
   OBJS= /usr/hhirf/fitu.o
         /tera/milner/Dfitu/usercmp.o
         /tera/milner/Dfitu/userfox.o
   #
   LIBS= /usr/hhirf/fitulib.a
         /usr/hhirf/dammlib.a
         /usr/hhirf/xglib.a
         /usr/hhirf/dammlib.a
         /usr/hhirf/xglib.a
         /usr/hhirf/milibb.a
         /usr/hhirf/orphlib.a
   #
   fitu: $(OBJS) $(LIBS)
   #
           f77  $(FFLAGS) $(OBJS) $(LIBS) -o fitu -lX11
 
 
                             Comments on Customizing
 
   o......You can  modify  USERCMP  &  USERFOX  to  create  your  own  set  of
          non-linear  functions. You just need to make sure that your versions
          of USERCMP & USERFOX are compatible with each other and the rest  of
          the package.
 
   o......Don't  change  COMMON/FTUSER/  since it is used by other routines in
          the package.
 
   o......Your version of USERCMP can communicate other  information  to  your
          version  of  USERFOX  via  other  user  defined common but don't use
          common labels ML..., XL..., FT..., MAINV or LLL since these  are  or
          may be defined by other routines in the package.
 
   o......Note  that  the  banner  labels  BANLAB  defined in USERCMP are just
          labels and have no effect on the calculations but they should be  be
          consistant with the associated functions in USERFOX.
    
   31-Mar-04 .... U620  FITU - A General 1-D Fitting Package - ...... PAGE  11
 
 
   U620.130  Example Non-linear Support Routine - USERCMP
 
   Example user command processor for non-linear fitting
   ===========================================================================
 
         SUBROUTINE USERCMP(IWD)
   C
         IMPLICIT NONE
   C
   C     ------------------------------------------------------------------
         COMMON/LLL/  MSSG(28),NAMPROG(2),LOGUT,LOGUP,LISFLG,MSGF
         INTEGER*4    MSSG,NAMPROG,LOGUT,LOGUP,LISFLG,MSGF
         CHARACTER*112 CMSSG
         EQUIVALENCE (CMSSG,MSSG)
   C     ------------------------------------------------------------------
         COMMON/FTUSER/ NONEG(64),NV,IFUNK,UTIT
         INTEGER*4      NONEG,    NV,IFUNK
         CHARACTER*40                      UTIT
   C
         DATA NONEG/64*0/     !Default - allow +/- for all coefficients
         DATA NV   /2/        !Default - 2 adjustable coefficients
         DATA IFUNK/2/        !Default - function ID=2
         DATA UTIT /'A+B*X'/  !Default - Banner label
   C     ------------------------------------------------------------------
         CHARACTER*40   BANLAB(50)
   C
         DATA BANLAB(1)/'A*X'/
         DATA BANLAB(2)/'A+B*X'/
         DATA BANLAB(3)/'A+B*X+C*X*X'/
         DATA BANLAB(4)/'A*DSQRT(X)'/
         DATA BANLAB(5)/'A+B*DSQRT(X)'/
         DATA BANLAB(6)/'A+B*DSQRT(X)+C*X'/
         DATA BANLAB(7)/'DSQRT(A+B*X)+C*X'/
         DATA BANLAB(8)/'A+B*X+C*DEXP(D*X)'/
         DATA BANLAB(9)/'A*(B/(C-B))*(EXP(-B*X)-EXP(-C*X))'/
   C     ------------------------------------------------------------------
         INTEGER*4      IWD(20),LWD(2,40),ITYP(40),NF,NTER
   C
         REAL*4         XV
   C
         INTEGER*4      IV,KIND,IERR,KMD,I
   C
         CHARACTER*8    FLAG
   C
         CHARACTER*18   POMFLAG
   C
         EQUIVALENCE    (KMD,LWD(1,1))
   C     ------------------------------------------------------------------
   C
         CALL GREAD(IWD,LWD,ITYP,NF,1,80,NTER)
   C
         IF(NTER.NE.0) GO TO 1000
   C
         IF(KMD.EQ.'FUNK') GO TO 5
         IF(KMD.EQ.'CPOS') GO TO 400
         IF(KMD.EQ.'CPON') GO TO 400
         IF(KMD.EQ.'CPOM') GO TO 400
         IF(KMD.EQ.'STAT') GO TO 500
   C
         GO TO 1010
   C
    
   31-Mar-04 .... U620  FITU - A General 1-D Fitting Package - ...... PAGE  12
 
 
   U620.130  Example Non-linear Support Routine - USERCMP (continued)
 
   C
       5 CALL MILV(LWD(1,2),IV,XV,KIND,IERR)     !Get function-ID
   C
         IF(IERR.NE.0) GO TO 1000                !Tst for error
   C
         IF(IV.LT.1)   GO TO 1020                !Tst for in range
         IF(IV.GT.9)   GO TO 1020                !tst for in range
   C
   C     ------------------------------------------------------------------
   C     Set up the specified user function
   C     ------------------------------------------------------------------
   C
         GO TO (10,20,30,40,50,60,70,80,90) IV   !Go set it up
   C
   C
      10 UTIT=BANLAB(1)                          !Display banner title
         NONEG(1)=0                              !Allow negative coeff-1
         IFUNK=1                                 !Function ID
         NV=1                                    !No. of coefficients
         RETURN
   C
      20 UTIT=BANLAB(2)                          !Display banner title
         NONEG(1)=0                              !Allow negative coeff-1
         NONEG(2)=0                              !Allow negative coeff-2
         IFUNK=2                                 !Function ID
         NV=2                                    !No. of coefficients
         RETURN
   C
      30 UTIT=BANLAB(3)                          !Display banner title
         NONEG(1)=0                              !Allow negative coeff-1
         NONEG(2)=0                              !Allow negative coeff-2
         NONEG(3)=0                              !Allow negative coeff-3
         IFUNK=3                                 !Function ID
         NV=3                                    !No. of coefficients
         RETURN
   C
      40 UTIT=BANLAB(4)                          !Display banner title
         NONEG(1)=0                              !Allow negative coeff-1
         IFUNK=4                                 !Function ID
         NV=1                                    !No. of coefficients
         RETURN
   C
      50 UTIT=BANLAB(5)                          !Display banner title
         NONEG(1)=0                              !Allow negative coeff-1
         NONEG(2)=0                              !Allow negative coeff-2
         IFUNK=5                                 !Function ID
         NV=2                                    !No. of coefficients
         RETURN
   C
      60 UTIT=BANLAB(6)                          !Display banner title
         NONEG(1)=0                              !Allow negative coeff-1
         NONEG(2)=0                              !Allow negative coeff-2
         NONEG(3)=0                              !Allow negative coeff-3
         IFUNK=6                                 !Function ID
         NV=3                                    !No. of coefficients
         RETURN
    
   31-Mar-04 .... U620  FITU - A General 1-D Fitting Package - ...... PAGE  13
 
 
   U620.130  Example Non-linear Support Routine - USERCMP (continued)
 
   C
      70 UTIT=BANLAB(7)                          !Display banner title
         NONEG(1)=1                              !Disallow neg   coeff-1
         NONEG(2)=1                              !Disallow neg   coeff-2
         NONEG(3)=0                              !Allow negative coeff-3
         IFUNK=7                                 !Function ID
         NV=3                                    !No. of coefficiemts
         RETURN
   C
      80 UTIT=BANLAB(8)                          !Display banner title
         NONEG(1)=0                              !Allow negative coeff-1
         NONEG(2)=0                              !Allow negative coeff-2
         NONEG(3)=0                              !Allow negative coeff-3
         NONEG(4)=1                              !Disallow neg   coeff-4
         IFUNK=8                                 !Function ID
         NV=4                                    !No. of coefficients
         RETURN
   C
      90 UTIT=BANLAB(9)                          !Display banner title
         NONEG(1)=0                              !Allow negative coeff-1
         NONEG(2)=0                              !Allow negative coeff-2
         NONEG(3)=0                              !Allow negative coeff-3
         IFUNK=9                                 !Function ID
         NV=3                                    !No. of coefficients
         RETURN
   C
   C     ------------------------------------------------------------------
   C     Display User Status
   C     ------------------------------------------------------------------
   C
     400 CALL MILV(LWD(1,2),IV,XV,KIND,IERR)
   C
         IF(IERR.NE.0) GO TO 1000
   C
         IF(IV.LT.1)   GO TO 1030
         IF(IV.GT.NV)  GO TO 1030
   C
         IF(KMD.EQ.'CPOS') NONEG(IV)=1
         IF(KMD.EQ.'CPON') NONEG(IV)=0
         IF(KMD.EQ.'CPOM') NONEG(IV)=0
   C
         RETURN
   C
    
   31-Mar-04 .... U620  FITU - A General 1-D Fitting Package - ...... PAGE  14
 
 
   U620.130  Example Non-linear Support Routine - USERCMP (continued)
 
   C
   C     ------------------------------------------------------------------
   C     Display User Status
   C     ------------------------------------------------------------------
   C
     500 WRITE(CMSSG,505)
     505 FORMAT('FUNK#  Function                                 Status')
         CALL MESSLOG(LOGUT,LOGUP)
         WRITE(CMSSG,510)
     510 FORMAT('--------------------------------------------------------')
         CALL MESSLOG(LOGUT,LOGUP)
         DO 530 I=1,9
         FLAG=' '
         IF(I.EQ.IFUNK) FLAG='SELECTED'
         WRITE(CMSSG,520)I,BANLAB(I),FLAG
     520 FORMAT(I5,'  ',A,' ',A)
         CALL MESSLOG(LOGUT,LOGUP)
         CALL MESSLOG(LOGUT,LOGUP)
     530 CONTINUE
   C
         WRITE(CMSSG,510)
         CALL MESSLOG(LOGUT,LOGUP)
         DO 550 I=1,NV
         POMFLAG='Pos or neg allowed'
         IF(NONEG(I).EQ.1) THEN
         POMFLAG='Pos only   allowed'
         ENDIF
         WRITE(CMSSG,535)POMFLAG,I
     535 FORMAT(A,' for coefficient# ',I2)
         CALL MESSLOG(LOGUT,LOGUP)
     550 CONTINUE
         RETURN
   C
   C     ------------------------------------------------------------------
   C     Send error messages
   C     ------------------------------------------------------------------
   C
    1000 WRITE(CMSSG,1005)
    1005 FORMAT('Syntax error or illegal value - command ignored')
         GO TO 2000
   C
    1010 WRITE(CMSSG,1015)
    1015 FORMAT('User command not recognized - command ignored')
         GO TO 2000
   C
    1020 WRITE(CMSSG,1025)
    1025 FORMAT('User function ID out of range - command ignored')
         GO TO 2000
   C
    1030 WRITE(CMSSG,1035)
    1035 FORMAT('User coefficient ID out of range - command ignored')
         GO TO 2000
   C
    2000 CALL MESSLOG(LOGUT,LOGUP)
         RETURN
         END
    
   31-Mar-04 .... U620  FITU - A General 1-D Fitting Package - ...... PAGE  15
 
 
   U620.140  Example Non-linear Support Routine - USERFOX
 
   Example user-supplied function for non-linear fitting
   ===========================================================================
 
         REAL*8 FUNCTION USERFOX(A,X)
   C
         IMPLICIT NONE
   C
   C     ------------------------------------------------------------------
         COMMON/FTUSER/ NONEG(64),NV,IFUNK,UTIT
         INTEGER*4      NONEG,    NV,IFUNK
         CHARACTER*40                      UTIT
   C     ------------------------------------------------------------------
         REAL*8         A(*),X,DENO,DABS
   C     ------------------------------------------------------------------
   C
         GO TO (10,20,30,40,50,60,70,80,90) IFUNK
   C
      10 USERFOX=A(1)*X
         RETURN
   C
      20 USERFOX=A(1) + A(2)*X
         RETURN
   C
      30 USERFOX=A(1) + A(2)*X + A(3)*X*X
         RETURN
   C
      40 USERFOX=A(1)*DSQRT(X)
         RETURN
   C
      50 USERFOX=A(1) + A(2)*DSQRT(X)
         RETURN
   C
      60 USERFOX=A(1) + A(2)*DSQRT(X) + A(3)*X
         RETURN
   C
      70 USERFOX=DSQRT(A(1) + A(2)*X) + A(3)*X
         RETURN
   C
      80 USERFOX=A(1) + A(2)*X + A(3)*DEXP(A(4)*X)
         RETURN
   C
      90 DENO=A(3)-A(2)
         IF(DABS(DENO).LT.1.0E-9) DENO=-1.0E-9
         USERFOX=A(1)*(A(2)/DENO)*(DEXP(-A(2)*X)-DEXP(-A(3)*X))
   C
         END
    
   31-Mar-04 .... U620  FITU - A General 1-D Fitting Package - ...... PAGE  16
 
 
 
   U620.150  Commands Related to Filename Variables, Symbols & Loops
 
   Filname Variables
 
   One  symbol  (integer  variable)  may  be  incorporated   in   a   FILENAME
   specification as the following examples illustrate:
 
   SYM=3
   IN FIL"SYM".DAT   ;Opens FIL3.DAT for input
 
   I=0
   LOOP 3
   I=I+1
   IN  FIL"I".DAT   ;Opens (in succession)  FIL1.DAT, FIL2.DAT, FIL3.DAT
   .
   .
   ENDLOOP
 
   LOOP execution and symbol definition
 
 
   Commands related to LOOP execution and SYMBOL definition
 
   SYM = EXPRESSION   Define symbol (SYM) up to 100 symbols supported
                      symbols M, N, O, P, Q, R, S are reserved
                      expression syntax is same as in CHIL
                      no imbedded blanks are allowed in expressions
                      symbols may contain up to 4 characters (5-8 ignored)
 
   DSYM               Displays list of currently defined sumbols & values
 
   LOOP N             Starts LOOP (executed N-times) N=SYM or CONST
   CMD  ....          Nesting supported
   CMD  ....          # lines between 1st LOOP & matching ENDL = 100
   ENDL               Defines end-of-loop
                      KILL (entered before ENDL) kills LOOP
                      Ctrl/C - aborts loop-in-progress
                      opening of CMD-file within a LOOP not allowed
    
   31-Mar-04 .... U620  FITU - A General 1-D Fitting Package - ...... PAGE  17
 
 
 
   U620.160  Comments
 
   (1)....Unless  you  have  a  very  small  number  of  data points to fit, I
          suggest that you create a file (fil.dat for example) which  contains
          the  data  sets to be fitted. After the program is started, open the
          file with the command - IN fil.dat
 
   (2)....Note that the data file does not contain actual  ID-number  entries.
          The  ID  referred  to in the FIT (or GO) command is just the ordinal
          number of the data set in the file. This may not be the best way  to
          do it but that's the way it is.
 
   (3)....If  your  fitting  procedure  will  involve numerous commands, it is
          probably best to create a command file (fil.cmd for example)  rather
          than  entering  them  at  run-time. If you have both a fil.dat and a
          fil.cmd, then all you have to do is:
 
   Type:  FITU
   Type:  IN   fil.dat
   Type:  CMD  fil.cmd
 
   And that's it.
